---
title: "Data_wrangling"
author: "Thijs Carrière"
date: "24-5-2024"
output: html_document
---

# 0. Introduction 

The code in this document prepares the raw data to the variables used in the analyses presented in the manuscript "The effects of personalized feedback on participant behavior in an app-based diary study". 

This first code block loads the packages used in this document and loads the data used.

```{r message=FALSE, warning=FALSE}
# Packages
library(tidyverse)
library(haven)
library(labelled)
library(lubridate)
library(chron)
library(ggplot2)
library(gridExtra)
library(caret)
library(patchwork)
library(ggpattern)
library(margins)

# Read in data

# Number of visits per screen
clicks <- read.csv("../Data/Data export 02-12-21/nl_paradataClicks.csv")

# App usage with time stamps
times <- read.csv("../Data/Data export 02-12-21/nl_paradataDateTimes.csv")

# Transaction data (data on the entries made in the app, both scans and manual entries)
transactions <- read.csv("../Data/Data export 02-12-21/NLtransplus.csv")

# Number of seconds per screen type
screen_times <- read.csv("../Data/Data export 02-12-21/nl_paradataScreenTimes.csv")

# Summary data
app_usage <- read.csv("../Data/Data export 02-12-21/NLhhsummary.csv")

# Background questionnaire
background <- read.csv("../Data/Data export 02-12-21/NLrespanalysis.csv")

```


# 1. Durations

We try to calculate duration times for each action. We filter per individual, and order the actions per date. Than the difference in time is calculated until the next action. Here, we did not yet account for different devices. The obtained times are seen as screentimes and are used as the primary data in the analysis of this study.

```{r}
# Split the times
data_new <- times

# Create variables where data can be stored
data_new$duration <- NA
data_new$day <- NA

data_save <- data_new[1,]


# Select the unique users
unique_users <- unique(data_new$userName)

# Calculate duration per person 
for(i in 1:length(unique_users)){
  data_pers <- data_new %>% filter(userName == unique_users[i])
  data_pers$duration <- NA
  data_pers <- data_pers[order(data_pers$time),]
  
  # Per person make the list
  for(j in 1:(nrow(data_pers)-1)){
    data_pers$duration[j] <- as.numeric(difftime(data_pers$time[j+1], data_pers$time[j], units = "secs"))
    data_pers$day[j] <- ceiling(as.numeric(difftime(data_pers$time[j], data_pers$time[1], units = "days")))
  }
  
  # merge the duration with the original frame
  data_save <- rbind(data_save, data_pers)
}

# Delete 'storage row'
data_save <- data_save[-1,]

# Save updated dataframe
write.csv(data_save, "../Thijs/time_frame.csv")
```

Next, we create subsets of data used further in the script

```{r}
# Make a subset of the insights screens
insights <- data_save %>% filter(objectName == "InsightsScreen")

# Separate data frame with days
days <- data_save %>% filter(objectName == "InsightsScreen")

# New labels for feedback
days$feedback <- NA
days$feedback[grep(".*delayed.*", days$groupName)] <- "delayed"
days$feedback[grep(".*all.*", days$groupName)] <- "instant"

# Rename the 'userName' variable
names(days)[names(days) == "userName"] <- "username"

```

# 2. Visit variables

The next block of code creates variables for the number of visits and mean duration of visits for each participant for each study phase.

```{r}
# Create list of usernames as storage object
active_users <- unique(days$username)
active_visits_df <- as.data.frame(active_users)
colnames(active_visits_df) <- c("username")

# Variables
active_visits_df$phase1_visits <- NA
active_visits_df$phase2_visits <- NA
active_visits_df$phase3_visits <- NA
active_visits_df$phase4_visits <- NA
active_visits_df$phase1_duration <- NA
active_visits_df$phase2_duration <- NA
active_visits_df$phase3_duration <- NA
active_visits_df$phase4_duration <- NA

# Calculate variables
for(i in 1:length(active_users)){
  pers <- days %>% filter(username == active_users[i]) %>% filter(duration > 4)
  
  # Calculate number of visits
  active_visits_df$phase1_visits[i] <- pers %>% filter(day == 1) %>% nrow()
  active_visits_df$phase2_visits[i] <- pers %>% filter(day > 1 & day < 8) %>% nrow()
  active_visits_df$phase3_visits[i] <- pers %>% filter(day > 7 & day < 14) %>% nrow()
  active_visits_df$phase4_visits[i] <- pers %>% filter(day > 13 & day < 20) %>% nrow()
  
  # Calculate average duration of visits
  pers_phase1 <- pers %>% filter(day == 1)
  active_visits_df$phase1_duration[i] <- mean(pers_phase1$duration, na.rm = T)
  
  pers_phase2 <- pers %>% filter(day > 1 & day < 8)
  active_visits_df$phase2_duration[i] <- mean(pers_phase2$duration, na.rm = T)
  
  pers_phase3 <- pers %>% filter(day > 7 & day < 14) 
  active_visits_df$phase3_duration[i] <- mean(pers_phase3$duration, na.rm = T)
  
  pers_phase4 <- pers %>% filter(day > 13 & day < 20)
  active_visits_df$phase4_duration[i] <- mean(pers_phase4$duration, na.rm = T)
}

# Adjust NaN with Na
active_visits_df <- active_visits_df %>% mutate_all(~ifelse(is.nan(.), NA, .))

# Link new variables to background data frame
background <- left_join(background, active_visits_df, by = "username")
```

Next, we calculate the last (meaningful) visit for each participant

```{r}
# Mark last visit / last meaningful visit
# Create saving object
days$last_day <- "no"
save <- days[1,]

for(i in 1:length(unique(days$username))){
  
  # filter days per person
  sub_days <- days %>% filter(username == unique(days$username)[i])
  sub_days$last_day[sub_days$day == max(sub_days$day)] <- "yes"
  
  # select only last day
  sub2 <- sub_days %>% filter(last_day == "yes")
  save <- rbind(save, sub2)
}

# Delete first row
max_day <- save[-1,]

# Filter out people that have multiple visits on their last day
max_day <- max_day %>% select(-time, -timestamp, -duration)
max_day <- unique(max_day)
```

```{r}
# Obtain the last active day for each participant that they had a look at their feedback
# Create saving object
days$last_day <- "no"
save <- days[1,]

for(i in 1:length(unique(days$username))){
  
  # filter days per person
  sub_days <- days %>% filter(username == unique(days$username)[i]) %>% 
    filter(day < 31)
  sub_days$last_day[sub_days$day == max(sub_days$day)] <- "yes"
  
  # select only last day
  sub2 <- sub_days %>% filter(last_day == "yes")
  save <- rbind(save, sub2)
}

# Delete first row
max_day4 <- save[-1,]

# Filter out people that have multiple visits on their last day
max_day4 <- max_day4 %>% select(-time, -timestamp, -duration)
max_day4 <- unique(max_day4)

# Frame with final visit (capped at 30 days)
maxDayFrame <- max_day4 %>% select(username, day)
colnames(maxDayFrame) <- c("username", "day_last_feedback_visit")
# The frames are combined in the code block 'add data on insights ...', below in this code
```

Next, we calculate the number of meaningful visits (= visits longer than 4 seconds) for each person, as well as the day of the first meaningful visit, the day of the last meaningful visit, and the number of meaningful visits after 14 days in the study

```{r, message=F, warning=F}
#### Calculate number of 'meaningful' feedback visits per person (= > 5 seconds)

# Storing object
number_meaningful <- as.data.frame(unique(days$username))
number_meaningful$amount <- NA
number_meaningful$first_meaningful <- NA
number_meaningful$last_meaningful <- NA
number_meaningful$after14 <- NA

# Calculate # of meaningful visits
for(i in 1:length(unique(days$username))){
  obj <- days %>% 
    filter(username == unique(days$username)[i]) %>% 
    filter(duration > 5)
  number_meaningful$amount[i] <- nrow(obj)
  
  # first and last meaningful visits
  obj2 <- obj %>% filter(day < 31)
  number_meaningful$first_meaningful[i] <- min(obj2$day, na.rm = T)
  number_meaningful$last_meaningful[i] <- max(obj2$day, na.rm = T)
  
  # number meaningful after 14 days
  obj3 <- obj %>% filter(day > 13)
  number_meaningful$after14[i] <- nrow(obj3)
}

# adjust colnames data frame, integrated at later point in code
colnames(number_meaningful) <- c("username", "meaningful_feedback_visits", "first_meaningful", "last_meaningful", "number_after14")

# replace inf-values with NA
number_meaningful$first_meaningful[is.infinite(number_meaningful$first_meaningful)] <- NA
number_meaningful$last_meaningful[is.infinite(number_meaningful$last_meaningful)] <- NA
``` 

# 3. Duration per person

The next block of code calculates the time each participant spent on their feedback screen, as well was their mean visit duration, the SD of their feedback duration and the number of visits.

```{r}
# Make form with all relevant people
people_frame <- days %>% select(username) %>% unique()
people_frame$ins_dur <- NA
people_frame$ins_mean <- NA
people_frame$ins_sd <- NA
people_frame$ins_n_dur

# Make list of names
people <- unique(days$username)

# Calculate per person the combined duration
for(i in 1:nrow(people_frame)){
  frame <- days %>% filter(username == people[i])
  people_frame$ins_dur[i] <- sum(frame$duration, na.rm = T)
  people_frame$ins_mean[i] <- mean(frame$duration, na.rm = T)
  people_frame$ins_sd[i] <- sd(frame$duration, na.rm = T)
  people_frame$ins_n_dur[i] <- nrow(frame)
}

# Rename columns
colnames(people_frame) <- c("username", "insights_dur", "insights_dur_mean", "insights_dur_sd", "insights_dur_n")

```

In the next code block, we compute the duration per phase and add this information to the background data frame.

```{r}
# obtain mean duration per phase
insight_pers <- as.data.frame(unique(insights$userName))
colnames(insight_pers) <- ("username")

# Create new variables
insight_pers$mean_dur1 <- NA
insight_pers$mean_dur2 <- NA
insight_pers$mean_dur3 <- NA
insight_pers$mean_dur4 <- NA

# Calculate variables
for(i in 1:nrow(insight_pers)){
  pers <- insights %>% filter(userName == insight_pers$username[i])
  
  phase_1 <- pers %>% filter(day == 1)
  insight_pers$mean_dur1[i] <- mean(phase_1$duration, na.rm = T)
  
  phase_2 <- pers %>% filter(day > 1 & day < 8)
  insight_pers$mean_dur2[i] <- mean(phase_2$duration, na.rm = T)
  
  phase_3 <- pers %>% filter(day > 7 & day < 14)
  insight_pers$mean_dur3[i] <- mean(phase_3$duration, na.rm = T)
  
  phase_4 <- pers %>% filter(day > 13)
  insight_pers$mean_dur4[i] <- mean(phase_4$duration, na.rm = T)
}

# Replace NaN to na
insight_pers <- insight_pers %>% mutate_all(~ifelse(is.nan(.), NA, .))

# Merge data with background
background <- left_join(background, insight_pers, by = "username")
```


# 4. Other variables 

In the next block of code, the last active day of the participants is calculated and added to a data frame.

```{r}
# final active day
perstest <- data_save %>% filter(userName == unique(data_save$userName)[1])
save <- as.data.frame(unique(data_save$userName))
save$lastactday <- NA
save$lastactday_cap30 <- NA

for(i in 1:length(unique(data_save$userName))){
  
  # Last active day after registering
  obj <- data_save %>% filter(userName == unique(data_save$userName)[i])
  save$lastactday[i] <- max(obj$day, na.rm = T)
  
  # Obtain last active day, within 30 days
  obj2 <- obj %>% filter(day < 31)
  save$lastactday_cap30[i] <- max(obj2$day, na.rm = T)
}

# make separate object for the information + rename vars
lastactiveday <- save
colnames(lastactiveday) <- c("username", "lastactday", "lastactday_cap30")
```

# 5. Variables on whether new data was added before viewing the data.

In the next block of code, we compute variables that show for each feedback visit whether new data was added before the visit.

```{r}
# change transaction times to correct format and lower by 2 hours to be compatible with the other data frames
transactions$transstart_dt <- ymd_hms(transactions$transstart)
transactions$transstart_dt <- transactions$transstart_dt - 7200

# Create username object to link data
userid <- background %>% select(username, dbuser)
colnames(userid) <- c("username", "user_id")

# add username to transactions
transactions <- left_join(transactions, userid, by = "user_id")

# overview of transaction moments
trans_small <- transactions %>% select(username, transstart_dt)

# Reclass timestamps in days frame
days$time_dt <- ymd_hms(days$time)

# calculate # of entries prior to check
days$nentries

for(i in 1:nrow(days)){
  small <- trans_small %>% filter(username == days$username[i])
  small2 <- small %>% filter(transstart_dt < days$time_dt[i])
  days$nentries[i] <- nrow(small2)
}

# Caculate number of new entries since last visit
days$newentries_n <- NA

for(i in 2:nrow(days)){
  if(days$username[i] == days$username[i - 1]){
    days$newentries_n[i] <- days$nentries[i] - days$nentries[i - 1]}
  else{
      days$newentries_n[i] <- days$nentries[i]
  }}

# Fix the first row
days$newentries_n[1] <- days$nentries[1]

# Indicate whether new entries are made
days$new_information <- "no"
days$new_information[days$newentries_n > 0] <- "yes"

```

# 6. Save the created variables as a new completed data frame

In the next code block, the created variables that were not yet added to the background data frame are added to the frame. The frame is then saved to be used for the analysis of the manuscript. 

```{r}
# Filter the number of clicks of the insightsScreen
insights_clicks <- clicks %>% filter(objectName == "InsightsScreen") %>% select(userName, clicks)
colnames(insights_clicks) <- c("username", "n_insight_clicks")

# Merge with background
background <- left_join(background, insights_clicks, by = "username")
background <- left_join(background, people_frame, by = "username")
background <- left_join(background, maxDayFrame, by = "username")
background <- left_join(background, number_meaningful, by = "username")
background <- left_join(background, lastactiveday, by = "username")

# Delete person that is in double
background <- background[!(background$username == "bQHJpHd" & background$n_insight_clicks == 1),]

# Obtain relevant variables
insights_data <- background %>% select(username, group, n_insight_clicks, insights_dur, insights_dur_mean, registered, active, day_last_feedback_visit, meaningful_feedback_visits, first_meaningful, last_meaningful, number_after14, nprod, nprodavg, scans, manual, ndevices, dayswithentry, activedays, lastactday, lastactday_cap30, mode)

# Save table to have data frame ready
write.csv(background, file = "../Thijs/background_vars.csv")

# Save days data frame as insights data
write.csv(days, "insights_added.csv")
```


