---
title: "Data_wrangling"
author: "Thijs Carrière"
date: "24-5-2024"
output: html_document
---

# 0. Introduction 

The code in this document prepares the raw data to the variables used in the analyses presented in the manuscript "The effects of personalized feedback on participant behavior in an app-based diary study". 

This first code block loads the packages used in this document and loads the data used.

```{r message=FALSE, warning=FALSE}
# Packages
library(tidyverse)
library(haven)
library(labelled)
library(lubridate)
library(chron)
library(ggplot2)
library(gridExtra)
library(caret)
library(patchwork)
library(ggpattern)
library(margins)

# Read in data

# Number of visits per screen
clicks <- read.csv("nl_paradataClicks.csv") # Insert correct file path

# App usage with time stamps
times <- read.csv("nl_paradataDateTimes.csv") # Insert correct file path

# Transaction data (data on the entries made in the app, both scans and manual entries)
transactions <- read.csv("NLtransplus.csv") # Insert correct file path

# Number of seconds per screen type
screen_times <- read.csv("nl_paradataScreenTimes.csv") # Insert correct file path

# Summary data
app_usage <- read.csv("NLhhsummary.csv") # Insert correct file path

# Background questionnaire
background <- read.csv("NLrespanalysis.csv") # Insert correct file path

```


# 1. Durations

We try to calculate duration times for each action. We filter per individual, and order the actions per date. Than the difference in time is calculated until the next action. Here, we did not yet account for different devices. The obtained times are seen as screentimes and are used as the primary data in the analysis of this study.

```{r}
# Split the times
data_new <- times

# Create variables where data can be stored
data_new$duration <- NA
data_new$day <- NA

data_save <- data_new[1,]


# Select the unique users
unique_users <- unique(data_new$userName)

# Calculate duration per person 
for(i in 1:length(unique_users)){
  data_pers <- data_new %>% filter(userName == unique_users[i])
  data_pers$duration <- NA
  data_pers <- data_pers[order(data_pers$time),]
  
  # Per person make the list
  for(j in 1:(nrow(data_pers)-1)){
    data_pers$duration[j] <- as.numeric(difftime(data_pers$time[j+1], data_pers$time[j], units = "secs"))
    data_pers$day[j] <- ceiling(as.numeric(difftime(data_pers$time[j], data_pers$time[1], units = "days")))
  }
  
  # merge the duration with the original frame
  data_save <- rbind(data_save, data_pers)
}

# Delete 'storage row'
data_save <- data_save[-1,]

# Save updated dataframe
write.csv(data_save, "time_frame.csv")
```

Next, we create subsets of data used further in the script

```{r}
# Make a subset of the insights screens
insights <- data_save %>% filter(objectName == "InsightsScreen")

# Separate data frame with days
days <- data_save %>% filter(objectName == "InsightsScreen")

# New labels for feedback
days$feedback <- NA
days$feedback[grep(".*delayed.*", days$groupName)] <- "delayed"
days$feedback[grep(".*all.*", days$groupName)] <- "instant"

# Rename the 'userName' variable
names(days)[names(days) == "userName"] <- "username"

```


# 2. Save the created variables as a new completed data frame

In the next code block, the created variables that were not yet added to the background data frame are added to the frame. The frame is then saved to be used for the analysis of the manuscript. 

```{r}
# Filter the number of clicks of the insightsScreen
insights_clicks <- clicks %>% filter(objectName == "InsightsScreen") %>% select(userName, clicks)
colnames(insights_clicks) <- c("username", "n_insight_clicks")

# Merge with background
background <- left_join(background, insights_clicks, by = "username")

# Delete person that is in double
background <- background[!(background$username == "bQHJpHd" & background$n_insight_clicks == 1),]

# Save table to have data frame ready
write.csv(background, file = "background_vars.csv")

# Save days data frame as insights data
write.csv(days, "insights_added.csv")
```

