---
title: "HBS feedback paper - Analysis script"
output: html_document
date: "2025-09-30"
---

# Introduction

In this document the code is provided for all analyses conducted in the paper 'Understanding app-diary study participant's interactions with feedback using in-app paradata' by Carrière et al. In the block below, relevant packages and required data files are loaded in.

```{r}
# Packages
library(tidyverse)
library(haven)
library(labelled)
library(lubridate)
library(chron)
library(ggplot2)
library(gridExtra)
library(caret)
library(patchwork)
library(ggpattern)
library(margins)
library(onewaytests)
library(coin)

# Import data - Insert correct data files and paths
days <- read.csv("insights_added.csv")[,-1] # Feedback visits and related paradata
background <- read.csv("background_vars.csv")[,-1] # Background characateristics of households
transactions <- read.csv("NLtransplus.csv")[,-1] # Substantive data on the data entries made

## Change the background feedback variable
background$feedback <- NA
background$feedback[grep(".*delayed.*", background$group)] <- "delayed"
background$feedback[grep(".*all.*", background$group)] <- "instant"
```

The following block of code filters out feedback visits that should not be included in the analysis. These are feedback visits shorter than 3.5 seconds, or feedback visits for the delayed feedback group before day 14. 

```{r}
# Filter the feedback visits from the frame that are not in the period that feedback was available.
days_clean <- days %>% filter(feedback == "instant" | (feedback == "delayed" & day > 13))

# Decide cutoff here
days_clean_cut <- days_clean %>% filter(duration > 3)

# Select users with feedback visits
visit_users <- days_clean_cut %>% select(username) %>% unique()

# New variables
visit_users$meaningful_visits_total <- NA
visit_users$meaningful_a14 <- NA
visit_users$mean_duration <- NA
visit_users$mean_duration_a14 <- NA

# Calculate variables
for(i in 1:nrow(visit_users)){
  frame <- days_clean_cut %>% filter(username == visit_users$username[i])
  
  visit_users$meaningful_visits_total[i] <- nrow(frame)
  visit_users$meaningful_a14[i] <- frame %>% filter(day > 13) %>% nrow()
  visit_users$mean_duration[i] <- mean(frame$duration, na.rm = T)
  frame_a14 <- frame %>% filter(day > 13)
  visit_users$mean_duration_a14[i] <- mean(frame_a14$duration, na.rm = T)
}

# Adjust for NaNs
visit_users$mean_duration_a14[is.nan(visit_users$mean_duration_a14) == T] <- 0

```

## Merge with background

In the following block of code we merge the background characteristics with the visit statistics per household.

```{r}
# New dataframe
background2 <- left_join(background, visit_users, by = c("username"))

# revalue 0's
active_2 <- background2 %>% filter(active == "TRUE")
active_2$meaningful_visits_total[is.na(active_2$meaningful_visits_total) == T] <- 0
active_2$meaningful_a14[is.na(active_2$meaningful_a14) == T] <- 0 
active_2$mean_duration[is.na(active_2$mean_duration) == T] <- 0 
active_2$mean_duration_a14[is.na(active_2$mean_duration_a14) == T] <- 0 

```


# Graphs

The following block of code provides the graphs that are presented in Figure 2 and Figure 3 of the manuscript.

```{r}
# Figure 1
ggplot(active_2) +
  geom_bar(aes(x = meaningful_visits_total, fill = feedback), position = position_dodge(preserve = "single")) +
  theme_minimal() +
  xlab("Number of feedback visits (>3.5 seconds)")

# Figure 2
# Summarize each day
mean_durations <- days %>%
  dplyr::filter(day < 26) %>%
  dplyr::group_by(day, feedback) %>% 
  dplyr::summarise("mean_duration" = mean(duration, na.rm = T), "sd" = sd(duration, na.rm = T)) %>%
  filter(feedback == "instant" | day > 13)

# Plot the mean duration per day
ggplot(data = mean_durations) +
  geom_col(aes(x = day, y = mean_duration, fill = feedback), position = position_dodge(preserve = "single")) +
  theme_minimal() +
  ylab("mean duration (s)")

```

## Summary stats

The following block of code provide the summary statistics of feedback visits as presented in section 4.2 of the manuscript. The second block of code tests for significant differences between feedback visit behavior after day 14 between the two feedback conditions, as also presented in section 4.2 of the manuscript. 

```{r}
# Summary visit statistics (# of visits; % never visited; mean visit duration; median visit duration)

## All instant feedback (include all)
active_instant_2 <- active_2 %>% filter(feedback == "instant")
mean(active_instant_2$meaningful_visits_total) # 5.73 average visits
table(active_instant_2$meaningful_visits_total)[1]/nrow(active_instant_2) # 13.4% never visited

mean(active_instant_2$mean_duration) # 13.64 (including 0, including only meaningful) seconds mean duration
median(active_instant_2$mean_duration) # 11.19 seconds median duration


## Instant feedback after day 14 (include completers)
mean(active_instant_2$meaningful_a14) # 1.67
table(active_instant_2$meaningful_a14)[1]/nrow(active_instant_2) # 42.9%

mean(active_instant_2$mean_duration_a14) # 8.36 (including 0, including only meaningful)
median(active_instant_2$mean_duration_a14) # 6.67


## Delayed feedback after day 14 (include completers)
active_del_2 <- active_2 %>% filter(feedback == "delayed")
mean(active_del_2$meaningful_a14) # 1.45
table(active_del_2$meaningful_a14)[1]/nrow(active_del_2) # 37.8%

mean(active_del_2$mean_duration_a14) # 11.20 (including 0s, only meaningful visits)
median(active_del_2$mean_duration_a14) # 10.5


## mean visit duration when only considering people who did visit (so not 0's)
active_instant_2 %>% filter(mean_duration > 0) %>% summarize(mean(mean_duration)) # 15.76 (all meaningful visits, only including participants with at least 1 visit)
active_instant_2 %>% filter(mean_duration > 0) %>% summarize(median(mean_duration))
active_instant_2 %>% filter(mean_duration_a14 > 0) %>% summarize(mean(mean_duration_a14)) # 14.63 (meaningful visits after day 14, only including participants with at least 1 feedback visit)
active_instant_2 %>% filter(mean_duration_a14 > 0) %>% summarize(median(mean_duration_a14))
active_del_2 %>% filter(mean_duration_a14 > 0) %>% summarize(mean(mean_duration_a14)) # 18.01 (meaningful visits after day 14, only including participants with at least 1 feedback visit)
active_del_2 %>% filter(mean_duration_a14 > 0) %>% summarize(median(mean_duration_a14))
```


```{r}
# Comparison tests between instant and delayed after day 14.

# T-test comparison corrected visiting times
a14_instant_times <- active_instant_2 %>% filter(mean_duration_a14 > 0)
a14_delayed_times <- active_del_2 %>% filter(mean_duration_a14 > 0)

## T-test comparisons
t.test(x = active_instant_2$meaningful_a14, y = active_del_2$meaningful_a14, var.equal = F) # t = .716, p = .475
t.test(x = a14_instant_times$mean_duration_a14, y = a14_delayed_times$mean_duration_a14, var.equal = F) # t = -1.92, p = 0.057


a14_all <- active_2 %>% filter(mean_duration_a14 > 0)
a14_all$feedback <- as.factor(a14_all$feedback)
median_test(mean_duration_a14 ~ feedback, data = a14_all) # z = 1.90, p = .057
wilcox.test(a14_instant_times$meaningful_a14, a14_delayed_times$meaningful_a14) # W = 2830.5, p = .560

active_a14_new <- active_2 %>% filter(complete == "TRUE")
table(active_a14_new$meaningful_a14, active_a14_new$feedback)
table(active_a14_new$feedback)

## Z-test comparisons of percentages
prop.test(x = c(31, 25), n = c(104, 99)) # x = .323, p = .570 (ins, del)

```

## Linear models

In the following blocks, we run the linear and logistic regressions presented in Table 1 of the manuscript. First, we revalue some of the variables for the model. In the second block, the actual models are run.

```{r}
# Revalue household size
active_2$householdsize <- case_when(active_2$TypeHH == "1. 1" ~ "1 person",
                                      active_2$TypeHH == "2. 2" ~ "more people",
                                      active_2$TypeHH == "3. 2+" ~ "more people",
                                      active_2$TypeHH == "4. 1+" ~ "more people",
                                      active_2$TypeHH == "5. overig" ~ "more people")

# Revalue income
active_2$income_num <- case_when(active_2$InkomenHH == "0. Missing" ~ NA,
                                   active_2$InkomenHH == "1. 0-20% perc" ~ 1,
                                   active_2$InkomenHH == "2. 20-40% perc" ~ 2,
                                   active_2$InkomenHH == "3. 40-60% perc" ~ 3,
                                   active_2$InkomenHH == "4. 60-80% perc" ~ 4,
                                   active_2$InkomenHH == "5. 80-100% perc" ~ 5,)

# Revalue age
active_2$leeftijd_num <- case_when(active_2$Leeftijd15 == "04. 18-24" ~ 21,
                                     active_2$Leeftijd15 == "05. 25-29" ~ 27,
                                     active_2$Leeftijd15 == "06. 30-34" ~ 32,
                                     active_2$Leeftijd15 == "07. 35-39" ~ 37,
                                     active_2$Leeftijd15 == "08. 40-44" ~ 42,
                                     active_2$Leeftijd15 == "09. 45-49" ~ 47,
                                     active_2$Leeftijd15 == "10. 50-54" ~ 52,
                                     active_2$Leeftijd15 == "11. 55-59" ~ 57,
                                     active_2$Leeftijd15 == "12. 60-64" ~ 62,
                                     active_2$Leeftijd15 == "13. 65-69" ~ 67,
                                     active_2$Leeftijd15 == "14. 70-74" ~ 72,
                                     active_2$Leeftijd15 == "15. >=75" ~ 77,)

```


```{r}
# Outcome variable for 'did visit at all'
active_2$did_watch <- case_when(active_2$meaningful_visits_total > 0 ~ "yes", 
                                  .default = "no")
active_2$did_watch <- as.factor(active_2$did_watch)

# First model to see who looks at all
mod1_visit <- glm(did_watch ~ feedback + income_num + leeftijd_num + householdsize + activedays + manual + scans + Geslacht + mode + nprodavg, data = active_2, family = "binomial")
summary(mod1_visit)
exp(mod1_visit$coefficients)

## Now split out the people that visited feedback for next models
active_watchers_2 <- active_2 %>% filter(did_watch == "yes")

# number of visits model
mod2_nvisit <- lm(meaningful_visits_total ~ feedback + income_num + leeftijd_num + householdsize + activedays + manual + scans + Geslacht + mode + nprodavg, data = active_watchers_2)
summary(mod2_nvisit)

# Time of visits model
mod3_duration <- lm(mean_duration ~ feedback + income_num + leeftijd_num + householdsize + activedays + manual + scans + Geslacht + mode + nprodavg, data = active_watchers_2)
summary(mod3_duration)
```


# Quality models

The following code blocks provides the results as provided in section 4.3 of the manuscript. 
The first block filters the relevant information from the transactions and makes it mergeable with the other files

```{r}
## Alter variables in the transaction data set for the analysis
# create new day-variable
transactions$full_day <- ceiling(transactions$transdays)

# change transaction times to correct format and lower by 2 hours to be compatible with the other data frames
transactions$transstart_dt <- ymd_hms(transactions$transstart)
transactions$transstart_dt <- transactions$transstart_dt - 7200

# Create username object to link data
userid <- background %>% select(username, dbuser, feedback)
colnames(userid) <- c("username", "user_id", "feedback")

# add username to transactions
transactions <- left_join(transactions, userid, by = "user_id")
```

The following block of code prepares the analysis on consistency of reporting, calculating the number of entries per study phase for each participant.

```{r}
# Add phase numbers to the transactions
transactions$phase <- case_when(transactions$full_day < 14 ~ "inclusion",
                                transactions$full_day > 13 ~ "exclusion")

transactions$phase <- factor(transactions$phase, levels = c("inclusion", "exclusion"))

# Create saving df
unique_users <- unique(transactions$username)

entry_phases <- as.data.frame(unique_users)
colnames(entry_phases) <- c("username")

# New variables in df
entry_phases$phase_incl <- NA
entry_phases$phase_excl <- NA

# Calculate numbers
for(i in 1:nrow(entry_phases)){
  pers <- transactions %>% filter(username == unique_users[i])
  
  entry_phases$phase_incl[i] <- pers %>% filter(phase == "inclusion") %>% nrow()
  entry_phases$phase_excl[i] <- pers %>% filter(phase == "exclusion") %>% nrow()
}

# join new data with background variables
active_watchers_2 <- left_join(active_watchers_2, entry_phases, by = "username")
active_2 <- left_join(active_2, entry_phases, by = "username")
```

In the next block, we calculate the other data quality measures per household. 

```{r}
# Variable for the average product price variance
transactions$prod_avg_price <- transactions$amount / transactions$nprod

# Create variables that capture variance in entry data
unique_users <- unique(transactions$username)

# Create df to store outcomes
data_quality <- as.data.frame(unique_users)
colnames(data_quality) <- c("username")

# New variables
data_quality$var_amount_incl <- NA
data_quality$mean_amount_incl <- NA
data_quality$var_prodavg_incl <- NA
data_quality$mean_prodavg_incl <- NA
data_quality$var_prodnum_incl <- NA
data_quality$mean_prodnum_incl <- NA


# Calculate outcomes per person
for(i in 1:length(unique_users)){
  pers <- transactions %>% filter(username == unique_users[i])
  
  inclusion <- pers %>% filter(full_day < 14)
  
  # Calculate per phase the variance variables
  data_quality$var_amount_incl[i] <- sd(inclusion$amount, na.rm = T)
  data_quality$mean_amount_incl[i] <- mean(inclusion$amount, na.rm = T)
  
  data_quality$var_prodavg_incl[i] <- sd(inclusion$prod_avg_price, na.rm = T)
  data_quality$mean_prodavg_incl[i] <- mean(inclusion$prod_avg_price, na.rm = T)
  
  data_quality$var_prodnum_incl[i] <- sd(inclusion$nprod, na.rm = T)
  data_quality$mean_prodnum_incl[i] <- mean(inclusion$nprod, na.rm = T)
}

# Merge new variables with old df
active_watchers_2 <- left_join(active_watchers_2, data_quality, by = "username")
active_2 <- left_join(active_2, data_quality, by = "username")
```

The next block compares the feedback conditions on the data quality measures.

```{r}
# amount spent per purchase
t.test(x = active_2$var_amount_incl[active_2$feedback == "instant"], y = active_2$var_amount_incl[active_2$feedback == "delayed"])

# Average product cost
t.test(x = active_2$var_prodavg_incl[active_2$feedback == "instant"], y = active_2$var_prodavg_incl[active_2$feedback == "delayed"])

# Average number of products
t.test(x = active_2$var_prodnum_incl[active_2$feedback == "instant"], y = active_2$var_prodnum_incl[active_2$feedback == "delayed"])

# Total entries made
t.test(x = active_2$phase_incl[active_2$feedback == "instant"], y = active_2$phase_incl[active_2$feedback == "delayed"], var.equal = F)
```

This last block provides the linear models that link data quality to feedback visit behavior.

```{r}
# Quality prediction models
qual_mod1 <- lm(var_amount_incl ~ mean_duration + meaningful_visits_total, data = active_watchers_2)
summary(qual_mod1)

qual_mod2 <- lm(var_prodavg_incl ~ mean_duration + meaningful_visits_total, data = active_watchers_2)
summary(qual_mod2)

qual_mod3 <- lm(var_prodnum_incl ~ mean_duration + meaningful_visits_total, data = active_watchers_2)
summary(qual_mod3)

qual_mod4 <- lm(phase_incl ~ mean_duration + meaningful_visits_total, data = active_watchers_2)
summary(qual_mod4)
```
